A Switching Planner for Combined Task and Observation Planning

### 2010-11-30 subarchitectures/planner.sa/trunk/src/latex/ICAPS-2011/switching.tex
Some graphics adjustments

  \tikzstyle{tree} = [sibling distance=4mm]
  \tikzstyle{toplevel} = [grow'=right, sibling distance=18mm]
  \tikzstyle{seclevel} = [sibling distance=8mm]
  \tikzstyle{pnode} = [diamond, draw=black, minimum size=2mm]
  \tikzstyle{cnode} = [circle, draw=black, minimum size=2.5mm]

>>>>

  \tikzstyle{tree} = [sibling distance=4.5mm]
  \tikzstyle{toplevel} = [grow'=right, sibling distance=22mm]
  \tikzstyle{seclevel} = [sibling distance=9mm]
  \tikzstyle{pnode} = [diamond, draw=black, minimum size=2.5mm]
  \tikzstyle{cnode} = [circle, draw=black, minimum size=3mm]
